---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  fig.align = "center"
)

library(ggplot2)
```

# devrel agent

A [commons agent](https://github.com/posit-dev/commons) for exploring the adoption, engagement, and growth of Posit open-source projects.

```{r}
#| echo: false
#| fig-alt: "A screencast of the devrel agent answering a question about CRAN downloads, then plotting downloads over time."
knitr::include_graphics(
  "https://github.com/user-attachments/assets/34449dea-3c57-4ecc-87ae-f68a219460fa"
)
```

```{r eval-data}
#| include: false

eval_samples <- read.csv("evals/results.csv")
eval_questions <- length(unique(eval_samples$id))
eval_results <- eval_samples |>
  dplyr::group_by(system) |>
  dplyr::summarise(
    `Mean accuracy (%)` = mean(score) * 100,
    `Median solver time (seconds)` = median(latency_sec),
    `Total cost (USD)` = sum(cost_usd),
    .groups = "drop"
  )
eval_results$system <- factor(
  eval_results$system,
  levels = c("Claude Code", "commons")
)
```

The agent is more accurate, faster, and cheaper on devrel-related questions than Claude Code placed in the devrel-io repository.

```{r eval-plot}
#| echo: false
#| fig-width: 10
#| fig-height: 4
#| fig-alt: "Three bar charts compare the devrel agent with Claude Code. The devrel agent has higher mean accuracy, lower median solver time, and lower total cost."
metric_columns <- c(
  "Mean accuracy (%)",
  "Median solver time (seconds)",
  "Total cost (USD)"
)
eval_plot <- stack(eval_results[metric_columns])
names(eval_plot) <- c("value", "metric")
eval_plot$system <- rep(
  eval_results$system,
  times = length(metric_columns)
)
accuracy <- eval_plot$metric == "Mean accuracy (%)"
eval_plot$value[accuracy] <- eval_plot$value[accuracy] / 100

eval_plot |>
  ggplot(aes(x = system, y = value, fill = system)) +
  geom_col(width = 0.7) +
  facet_wrap(vars(metric), scales = "free_y") +
  scale_fill_manual(
    values = c("Claude Code" = "grey85", "commons" = "#438EB5"),
    guide = "none"
  ) +
  scale_y_continuous(
    labels = \(x) {
      if (max(x, na.rm = TRUE) <= 1) {
        paste0(x * 100, "%")
      } else {
        format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
      }
    }
  ) +
  labs(
    x = NULL,
    y = NULL,
    caption = paste(
      eval_questions,
      "questions across three epochs. Higher accuracy is better. Lower time and cost are better."
    ),
    title = "The devrel agent was more accurate, faster, and cheaper than Claude Code"
  ) +
  theme_minimal()
```

The agent analyzes the [devrel-io](https://github.com/posit-dev/devrel-io) data, which is an automated collection of devrel metrics. devrel-io is built with [posit-dev/velocirepo](https://github.com/posit-dev/velocirepo), a more general data synthesis software.
